Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-02-23 paper.tex
mas correcciones de Dorso

We find these topological magnitudes useful for comparing the 
\textcolor{blue}{pedestrian behavior in the} 
corridor geometry with respect to the bottleneck geometry. A re-examination of 
Fig.~\ref{degree_dens} (corridor) and Fig.~\ref{degree_vd} (bottleneck) reveal 
that the pedestrian stiffness $k_n$ affects differently the way they contact 
each other. The mean degree increases for ``stiff'' pedestrians moving along 
the corridor (at densities above $5\,$p/m$^2$). Conversely, the mean degree 
increases for ``soft'' pedestrians in the bottleneck situation.\\

@@

The above results correspond to \textcolor{blue}{\sout{a milestone} an important step} in the 
investigation. The \textcolor{blue}{inter-pedestrian} connectivity differences between the bottleneck geometry 
and the corridor geometry were not expected and opens two major questions:
\textcolor{blue}{\sout{ how 
does the body stiffness interact with the walls} do the pedestrians interact with the walls as
a function of the body stiffness}, and consequently, how does 
this affect the flux across the corridor.\\

@@

The crowd behaves like a solid for very stiff pedestrians. This means that the crowd can not be easily ``deformed''. In this context, deformation means that parts of the crowd may be \textcolor{blue}{\sout{released} allowed} to move faster than other parts of the crowd. \\

@@

Our efforts to ``tune'' the original SFM to \textcolor{blue}{reproduce} empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.  We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$. Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal. We encourage further research to find dimensionless numbers that may better fit experimental data.\\

>>>>

We find these topological magnitudes useful for comparing the 
\textcolor{blue}{pedestrian behavior in the} 
corridor geometry with respect to the bottleneck geometry. A re-examination of 
Fig.~\ref{degree_dens} (corridor) and Fig.~\ref{degree_vd} (bottleneck) reveal 
that the pedestrian stiffness $k_n$ affects differently the way they contact 
each other. The mean degree increases for ``stiff'' pedestrians moving along 
the corridor \textcolor{blue}{\sout{(at densities above} 
as the density increased with a sharp increase at} $5\,$p/m$^2$\textcolor{blue}{\sout{)}}. Conversely, the mean degree 
increases for ``soft'' pedestrians in the bottleneck situation.\\

@@

The above results correspond to \textcolor{blue}{\sout{a milestone} an important step} in the 
investigation. The \textcolor{blue}{inter-pedestrian} connectivity differences between the bottleneck geometry 
and the corridor geometry were not expected and opens two major questions:
\textcolor{blue}{\sout{ how 
does the body stiffness interact with the walls} how do the pedestrians interact with the walls as
a function of the body stiffness}, and consequently, how does 
this affect the flux across the corridor.\\

@@

\textcolor{blue}{From the results displayed above, we realize that \sout{The} the} crowd behaves like a solid for very stiff pedestrians. This means that the crowd can not be easily ``deformed''. In this context, deformation means that parts of the crowd may be \textcolor{blue}{\sout{released} allowed} to move faster than other parts of the crowd. \\

@@

Our efforts to ``tune'' the original SFM to \textcolor{blue}{reproduce} empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.  We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{•}hcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$. Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal. We encourage further research to find dimensionless numbers that may better fit experimental data.\\
